Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-11-22 paper/main.tex
naming the reviewers

This paper has undergone internal review in the LSST Dark Energy Science Collaboration.%, the internal reviewers were: Daniel Gruen, Markus Rau, and Michael Troxel. % REQUIRED if true

@@

The authors express gratitude to Alex Abate, without whom this paper would not have gotten started.
% The authors would like to thank their LSST-DESC publication review committee for comments that improved the paper draft.
% hack event acknowledgments are important
%We thank Stony Brook University for hosting the Summer 2017 LSST-DESC Hack Day at which this work was partially completed.

>>>>

This paper has undergone internal review in the LSST Dark Energy Science Collaboration.
The authors acknowledge feedback from the internal reviewers: Daniel Gruen, Markus Rau, and Michael Troxel. % REQUIRED if true

@@

The authors express immense gratitude to Alex Abate, without whom this paper would not have gotten started.
% The authors would like to thank their LSST-DESC publication review committee for comments that improved the paper draft.
% hack event acknowledgments are important
%We thank Stony Brook University for hosting the Summer 2017 LSST-DESC Hack Day at which this work was partially completed.
